Democracy, Public Support, and Measurement Uncertainty

### 2021-06-11 paper/dcpo_demsupport_appendix.Rmd
finish comparison plots

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, dpi = 300)

@@

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools, # analysis
  plm,
  glue,
  huxtable, kableExtra, modelsummary, # tabulation
  latex2exp, # visualization
  rstan, # Bayesian estimation
  tidyverse # data wrangling
)

@@

## Claassen Replication Input

@@

```{r claassen_m5_theta}
load(here::here("data", "claassen_m5.rda"))

claassen_m5_theta <- rstan::extract(claassen_m5, pars = "theta")

save(claassen_m5_theta, file = "data/claassen_m5_theta.rda")

claassen_m5_x_pred <- rstan::extract(claassen_m5, pars = "x_pred")

save(claassen_replication_input, claassen_m5_x_pred, file = "data/claassen_m5_x_pred.rda")
```

```{r claassenUncertainty, cache=TRUE}
load(here::here("data", "claassen_m5_3k_07-05-11-16.rda")) # ours

claassen_m5_theta <- rstan::extract(claassen_m5, pars = "theta")

ls_year <- 1988:2017
ls_country <- claassen_input$data$country %>% unique()

@@

claassen_m5_theta_std = (claassen_m5_theta[[1]] - mean(as.vector(claassen_m5_theta[[1]]))) / sd(as.vector(claassen_m5_theta[[1]]))

df_theta <- purrr::map(1:1000, function(x) {
  claassen_m5_theta_std[x,,] %>% 
    as_tibble() %>% 
    rename_with(~ls_country, .cols = starts_with("V")) %>% 
    mutate(year = first_year + row_number() - 1) %>% 
    pivot_longer(cols = !year,
                 names_to = "country",
                 values_to = "theta") %>%
    arrange(country, year) %>% 
    left_join(sd_controls, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

@@

  if (class(result)[[1]] == "plm") {
     mutate(df_result, std.error = vcovBK_se(result))
  } else{
    mutate(df_result, std.error = vcovHC_se(result))
  }

@@

map_df(1:2, function(a) {
  result_cls[[a]][[1]] %>% 
    mutate(model = if_else(a==1, "Ours", "Claassen's"),
           term = str_replace(term, "SupDem_trim", "theta_mean")) %>% 
    filter(!str_detect(term, "(Intercept)"))
}) %>% 
  dotwhisker::dwplot() %>% 
  relabel_predictors(c(`plm::lag(Libdem_VD, 1:2)1` = "Democracy(t-1)",
                       `plm::lag(Libdem_VD, 1:2)2` = "Democracy(t-2)",
                       `plm::lag(theta_mean, 1)` = "Democratic Mood(t-1)",
                       `plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t-1)",
                       `plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t-1)",
                       `plm::lag(Libdem_regUN, 1)` = "Regional Democracy(t-1)",
                       `plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)", #there's a lag in the replication file
                       `plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t-1)")) +
  geom_vline(xintercept = 0, colour = "grey80", linetype = 2) +
  theme_minimal() +
  ggtitle("Dependent Variable: Level of Democracy") + 
  xlab("Coefficient Estimate") +
  scale_color_discrete(name="Dataset")

ggsave("paper/ours_vs_claassens_mean.pdf")

@@

load(here::here("data", "pure_claassen_1k_result.rda"))

df_result_cls_1k <- summary(mitools::MIcombine(results = result_betas_m5_1k, 
                                               variance = result_vars_m5_1k)) %>%
  rownames_to_column(var = "term") %>% 
  rename(conf.low = `(lower`,
         conf.high = `upper)`, 
         estimate = results) %>% 
  filter(!str_detect(term, "(Intercept)")) %>% 
  mutate(model = "Ours")

bind_rows(df_result_cls_1k, mod.1_df_result_cls_1k) %>% 
  dotwhisker::dwplot() %>% 
  relabel_predictors(c(`plm::lag(Libdem_VD, 1:2)1` = "Democracy(t-1)",
                       `plm::lag(Libdem_VD, 1:2)2` = "Democracy(t-2)",
                       `plm::lag(theta, 1)` = "Democratic Mood(t-1)",
                       `plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t-1)",
                       `plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t-1)",
                       `plm::lag(Libdem_regUN, 1)` = "Regional Democracy(t-1)",
                       `plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)", #there's a lag in the replication file
                       `plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t-1)")) +
  geom_vline(xintercept = 0, colour = "grey80", linetype = 2) +
  theme_minimal() +
  ggtitle("Dependent Variable: Level of Democracy") + 
  xlab("Coefficient Estimate") +
  scale_color_discrete(name="1k Samples\nDataset", breaks=c("Claassen's","Ours"))

ggsave("paper/ours_vs_claassens_1k.pdf")
```

\pagebreak

>>>>

knitr::opts_chunk$set(cache = TRUE, echo = FALSE, message = FALSE, warning = FALSE, dpi = 300, include = FALSE)

@@

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools, # analysis
  plm,
  glue, dotwhisker,
  huxtable, kableExtra, modelsummary, # tabulation
  latex2exp, patchwork, # visualization
  rstan, # Bayesian estimation
  tidyverse # data wrangling
)

@@

## Claassen Replication

@@

```{r ajps_mean}
load(here::here("data", "claassen_m5_3k_07-05-11-16.rda")) # our dataset of estimates, from surveys & DCPOtools, as generated in above (unrun) chunks

claassen_m5_theta <- rstan::extract(claassen_m5, pars = "theta") %>% 
  first()

ls_year <- 1988:2017
ls_country <- unique(claassen_input$data$country)

@@

# standardize, exactly as in 'supdem stan estimation ajps.R' at L192
claassen_m5_theta_std = (claassen_m5_theta - mean(as.vector(claassen_m5_theta))) / sd(as.vector(claassen_m5_theta))

@@

  if (class(result)[[1]] == "plm") {
     mutate(df_result, std.error = vcovBK_se(result))
  } else {
    mutate(df_result, std.error = vcovHC_se(result))
  }

@@

ajps_mean_plot <- map_df(1:2, function(a) {
  result_cls[[a]][[1]] %>% 
    mutate(model = if_else(a==1, "Ours", "Claassen's"),
           term = str_replace(term, "SupDem_trim", "theta_mean")) %>% 
    filter(!str_detect(term, "(Intercept)"))
}) %>% 
  dotwhisker::dwplot() %>% 
  relabel_predictors(c(`plm::lag(Libdem_VD, 1:2)1` = "Democracy(t-1)",
                       `plm::lag(Libdem_VD, 1:2)2` = "Democracy(t-2)",
                       `plm::lag(theta_mean, 1)` = "Democratic Mood(t-1)",
                       `plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t-1)",
                       `plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t-1)",
                       `plm::lag(Libdem_regUN, 1)` = "Regional Democracy(t-1)",
                       `plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)", #there's a lag in the replication file
                       `plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t-1)")) +
  geom_vline(xintercept = 0, colour = "grey80", linetype = 2) +
  theme_minimal() +
  ggtitle("Dependent Variable: Level of Democracy") + 
  xlab("Coefficient Estimate") +
  scale_color_discrete(name="Dataset", breaks=c("Claassen's","Ours"))
```

```{r our_ajps_1k}
df_theta <- purrr::map(1:1000, function(x) {
  claassen_m5_theta_std[x,,] %>% 
    as_tibble() %>% 
    rename_with(~ls_country, .cols = starts_with("V")) %>% 
    mutate(year = first_year + row_number() - 1) %>% 
    pivot_longer(cols = !year,
                 names_to = "country",
                 values_to = "theta") %>%
    arrange(country, year) %>% 
    left_join(sd_controls, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

@@

df_result_cls_1k <- summary(mitools::MIcombine(results = result_betas_m5_1k, 
                                               variance = result_vars_m5_1k)) %>%
  rownames_to_column(var = "term") %>% 
  rename(conf.low = `(lower`,
         conf.high = `upper)`, 
         estimate = results) %>% 
  filter(!str_detect(term, "(Intercept)")) %>% 
  mutate(model = "Ours")
```

```{r pure_claassen_ajps_1k}
load(here::here("data", "pure_claassen_1k_result.rda")) # from pure_claassen.R
# Replicate Claassen AJPS thetas, using his input data and his code
# light revision of 'supdem stan estimation ajps.R'

# options
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())

# read support for dem data
sddem1 = read.csv(here::here("data", "supdem raw survey marginals.tab"))

# remove NAs
sddem1 = sddem1[!sddem1$Response==0, ]

# create year by country indicators
year0 = 1987
sddem1 = sddem1[sddem1$Year > year0,]
sddem1 = unite(sddem1, YearCountry, c(Year, Country), sep = "_", remove = FALSE)

# create item by country indicators
sddem1 = unite(sddem1, ItemCnt, c(Item, Country), sep = "_", remove = FALSE)

# create year by project indicators
sddem1 = unite(sddem1, YrProj, c(Year, Project), sep = "_", remove = FALSE)

# create year by project by country indicators
sddem1 = unite(sddem1, YrProjCnt, c(YrProj, Country), sep = "_", remove = FALSE)

# factorise
sddem1$Country = as.factor(as.character(sddem1$Country))
sddem1$Item = as.factor(as.character(sddem1$Item))
sddem1$ItemCnt = as.factor(as.character(sddem1$ItemCnt))
sddem1$Project = as.factor(as.character(sddem1$Project))
sddem1$YrProj = as.factor(as.character(sddem1$YrProj))
sddem1$YrProjCnt = as.factor(as.character(sddem1$YrProjCnt))
sddem1$Year = sddem1$Year-year0

# count data
dim(sddem1)[1]                   # 3765 national responses
length(unique(sddem1$Country))   # 150 countries
length(unique(sddem1$Project))   # 14 projects
length(unique(sddem1$Item))      # 52 items
length(unique(sddem1$ItemCnt))   # 1453 item-country
length(unique(sddem1$YrProjCnt)) # 1390 national surveys
length(unique(sddem1$Year))      # 27 unique years (out of 30)
sum(sddem1$Sample) / dim(sddem1)[1] * length(unique(sddem1$YrProjCnt))   # 1,804,450 respondents

# drop countries with less than 2 years of data
cnt.obs.years = rowSums(table(sddem1$Country, sddem1$Year) > 0)
sort(cnt.obs.years)
sddem2 = sddem1[sddem1$Country %in% levels(sddem1$Country)[cnt.obs.years > 1], ]
length(unique(sddem2$Country))   # 137 countries with 2+ years of data

#### Stan estimation
# prepare data for stan
n.items = length(unique(sddem2$Item))
n.cntrys = length(unique(sddem2$Country))
n.yrs = 2017-year0
n.proj = length(unique(sddem2$Project))
n.resp = dim(sddem2)[1]
n.itm.cnt = length(unique(sddem2$ItemCnt))
n.cntry.yrs = n.cntrys * n.yrs
n.yr.proj.cnt = length(unique(sddem2$YrProjCnt))
cntrys = as.numeric(factor(sddem2$Country))
cnt.names = as.character(sort(unique(sddem2$Country)))
cnt.code = as.character(sddem2[match(cnt.names, sddem2$Country), "CAbb"])
cnt.code[83] = "MNE"
cnt.code[106] = "SRB"
items = as.numeric(factor(sddem2$Item))
yrs = sddem2$Year
projs = as.numeric(factor(sddem2$Project))
itm.cnts = as.numeric(factor(sddem2$ItemCnt))

# specify data for stan
dat.2 = list(N=n.resp, K=n.items, T=n.yrs, J=n.cntrys, P=n.itm.cnt, jj=cntrys, tt=yrs, 
             pp=itm.cnts, kk=items, x=sddem2$Response, samp=sddem2$Sample)
sapply(dat.2, summary)

# pars
pars.5 = c("mu_lambda","sigma_lambda","sigma_delta","sigma_theta","phi","lambda","delta","theta",
           "x_pred","log_lik")

save(dat.2, pars.5, file = here::here("R", "argon", "dcpo_demsupport_rep", "data", "pure_claassen.rda"))

# run 'R/argon/dcpo_demsupport_rep/R/pure_claassen_m5.R'
stan.mod.5 <- rio::import(here::here("R", "argon", "dcpo_demsupport_rep", "data", "pure_claassen_m5.rda"))

#### Extract theta estimates

theta.out = rstan::extract(stan.mod.5, pars = c("theta"))[[1]]
theta.std = (theta.out - mean(as.vector(theta.out))) / sd(as.vector(theta.out)) # standardize
theta.out.t = apply( theta.std, 1, function(x) t(x) )
theta.out.df = data.frame(Country=rep(cnt.names, length.out=n.cntrys*30), 
                          ISO_code=rep(cnt.code, length.out=n.cntrys*30),
                          Year=rep(1988:2017, each=n.cntrys), theta.out.t)
theta.pe = theta.out.df[,1:3]
theta.dim = dim(theta.out.df)[2]
theta.pe$SupDem_trim = apply(theta.out.df[,4:theta.dim], 1, mean)

first.yr = data.frame(Country=levels(sddem2$Country),
                      First_yr = as.vector(by(sddem2, sddem2$Country, function(x) min(as.numeric(x$Year))+1987)))

theta.pe = merge(theta.pe, first.yr, by="Country", all.x=TRUE)
cnts = theta.pe[theta.pe$Year==2008, "Country"]
frst.yr = theta.pe[theta.pe$Year==2008, "First_yr"]
for(i in 1:length(cnts)) {
    theta.pe[theta.pe$Country==cnts[i] & theta.pe$Year<frst.yr[i], "SupDem_trim"] = NA
}

sd_controls <- read_csv(here::here("data", "Support_democracy_ajps.csv"),
                        col_types = cols(.default = col_double(),
                                         Country = col_character(),
                                         Cnt_code = col_character(),
                                         ISO_code = col_character(),
                                         Region_UN = col_character()))

theta.out.df_list <- map(1:1000, function(x) {
    theta.pe %>% 
        mutate(theta0 = theta.out.t[,x],
               theta = if_else(!is.na(SupDem_trim), theta0, NA_real_)) %>% 
        left_join(sd_controls, by = c("Country", "Year")) %>% 
        plm::pdata.frame(index = c("Country", "Year"))
})

mod.1_1k <- map(theta.out.df_list, function(aDataset) {
    plm(Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + plm::lag(theta, 1) + plm::lag(lnGDP_imp, 1) +
            plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) +
            plm::lag(Res_cp_WDI_di, 1), model="pooling", data = aDataset)
})

result_betas_mod.1_1k <- mitools::MIextract(mod.1_1k, fun = coef)
result_vars_mod.1_1k <- mitools::MIextract(mod.1_1k, fun = vcovBK_se)

mod.1_df_result_cls_1k <- summary(mitools::MIcombine(results = result_betas_mod.1_1k,
                                            variance = result_vars_mod.1_1k)) %>%
    rownames_to_column(var = "term") %>% 
    rename(conf.low = `(lower`,
           conf.high = `upper)`, 
           estimate = results) %>% 
    filter(!str_detect(term, "(Intercept)")) %>% 
    mutate(model = "Claassen's")
```

```{r ajps_1k_plot}
ajps_1k_plot <- bind_rows(df_result_cls_1k, mod.1_df_result_cls_1k) %>% 
  dotwhisker::dwplot() %>% 
  relabel_predictors(c(`plm::lag(Libdem_VD, 1:2)1` = "Democracy(t-1)",
                       `plm::lag(Libdem_VD, 1:2)2` = "Democracy(t-2)",
                       `plm::lag(theta, 1)` = "Democratic Mood(t-1)",
                       `plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t-1)",
                       `plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t-1)",
                       `plm::lag(Libdem_regUN, 1)` = "Regional Democracy(t-1)",
                       `plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)", #there's a lag in the replication file
                       `plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t-1)")) +
  geom_vline(xintercept = 0, colour = "grey80", linetype = 2) +
  theme_minimal() +
  ggtitle("Dependent Variable: Level of Democracy") + 
  xlab("Coefficient Estimate") +
  scale_color_discrete(name="1k Samples\nDataset", breaks=c("Claassen's","Ours"))
```

```{r apsr_mean}
if (!file.exists(here::here("data", "dem_mood_apsr.csv"))) {
  tempfile <- dataverse::get_file("dem_mood_apsr.tab", "doi:10.7910/DVN/FECIO3", 
                                  format = "original") # Claassen's APSR replication file

  writeBin(tempfile, here::here("data", "dem_mood_apsr.csv"))
}

sd_controls_apsr <- read_csv(here::here("data", "dem_mood_apsr.csv"), 
                        col_types = cols(.default = col_double(),
                                         Country = col_character(),
                                         ISO_code = col_character(),
                                         Region_UN = col_character())) %>% 
  mutate(country = countrycode::countrycode(as.character(Country), "country.name", "country.name"),
         year = as.numeric(as.character(Year))) %>% 
  left_join(first_years, by = "country") %>% 
  filter(year >= first_year)

df_theta_mean_apsr <- purrr::map_df(1:1000, function(x) {
  claassen_m5_theta_std[x,,] %>% 
    as_tibble() %>% 
    rename_with(~ls_country, .cols = starts_with("V")) %>% 
    mutate(year = first_year + row_number() - 1) %>% 
    pivot_longer(cols = !year,
                 names_to = "country",
                 values_to = "theta") %>%
    arrange(country, year)
}) %>% 
  group_by(country, year) %>% 
  summarize(theta_mean = mean(theta)) %>% 
  right_join(sd_controls_apsr, by = c("country", "year")) %>% 
  plm::pdata.frame(index = c("country", "year"))

cor(df_theta_mean$theta_mean, df_theta_mean_apsr$theta_mean) # 1

ls_dv_apsr <- c("theta_mean", "SupDem_trim")

ls_eq_apsr <- glue::glue("diff({ls_dv_apsr}, lag=1) ~ plm::lag({ls_dv_apsr}, 1:2) + diff(Libdem_z, lag=1) + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag=1) + plm::lag(lnGDP_imp, 1)")

ls_mod_apsr <- glue::glue("plm({ls_eq_apsr}, model = 'pooling', data = df_theta_mean_apsr)")

df_result_cls_apsr <- map(ls_mod_apsr, function(mod) {
  result <- eval(parse(text = mod))
})

tidy_cls_apsr <- map(df_result_cls_apsr, function(result) {
  df_result <- tidy(result, conf.int = TRUE)

  if (class(result)[[1]] == "plm") {
     mutate(df_result, std.error = vcovBK_se(result))
  } else {
    mutate(df_result, std.error = vcovHC_se(result))
  }
})

glance_cls_apsr <- map(df_result_cls_apsr, function(aResult) {
  if (class(aResult)[[1]] == "plm") { 
    glance.plm(aResult) # using the customized glance function
  } else {
    glance(aResult)
  }
})

result_cls_apsr <- map2(tidy_cls_apsr, glance_cls_apsr, ~ list(.x, .y))
#names(result_cls) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")

apsr_mean_plot <- map_df(1:2, function(a) {
  result_cls_apsr[[a]][[1]] %>% 
    mutate(model = if_else(a==1, "Ours", "Claassen's")) %>% 
    filter(!str_detect(term, "(Intercept)"))
}) %>% 
  dotwhisker::dwplot() %>% 
  relabel_predictors(c(`plm::lag(theta_mean, 1:2)1` = "Support[t-1]",
                       `plm::lag(theta_mean, 1:2)2` = "Support[t-2]",
                       `plm::lag(SupDem_trim, 1:2)1` = "Support[t-1]",
                       `plm::lag(SupDem_trim, 1:2)2` = "Support[t-2]",
                       `diff(Libdem_z, lag = 1)` = "Delta~Liberal~democracy",
                       `plm::lag(Libdem_z, 1)` = "Liberal~democracy[t-1]",
                       `diff(lnGDP_imp, lag = 1)` = "Delta~Log GDP per capita",
                       `plm::lag(lnGDP_imp, 1)` = "Log GDP per capita[t-1]")) +
  geom_vline(xintercept = 0, colour = "grey80", linetype = 2) +
  theme_minimal() +
  ggtitle("Dependent Variable: Delta Support for Democracy") + 
  xlab("Coefficient Estimate") +
  scale_color_discrete(name="Dataset", breaks=c("Claassen's","Ours"))
```

```{r apsr_1k}
df_theta_apsr <- purrr::map(1:1000, function(x) {
  claassen_m5_theta_std[x,,] %>% 
    as_tibble() %>% 
    rename_with(~ls_country, .cols = starts_with("V")) %>% 
    mutate(year = first_year + row_number() - 1) %>% 
    pivot_longer(cols = !year,
                 names_to = "country",
                 values_to = "theta") %>%
    arrange(country, year) %>% 
    left_join(sd_controls_apsr, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

result_m5_1k_apsr <- map(df_theta_apsr, function(aDataset) {
  plm(diff(theta, lag=1) ~ plm::lag(theta, 1:2) + diff(Libdem_z, lag=1) 
           + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag=1) + plm::lag(lnGDP_imp, 1), 
           aDataset, model="pooling")
})

result_betas_m5_1k_apsr <- mitools::MIextract(result_m5_1k_apsr, fun = coef)
result_vars_m5_1k_apsr <- mitools::MIextract(result_m5_1k_apsr, fun = vcovBK_se)

df_result_cls_1k_apsr <- summary(mitools::MIcombine(results = result_betas_m5_1k_apsr, 
                                                    variance = result_vars_m5_1k_apsr)) %>%
  rownames_to_column(var = "term") %>% 
  rename(conf.low = `(lower`,
         conf.high = `upper)`, 
         estimate = results) %>% 
  filter(!str_detect(term, "(Intercept)")) %>% 
  mutate(model = "Ours")
```

```{r pure_claassen_apsr_1k}
sd.apsr = read.csv(here::here("data", "dem_mood_apsr.csv")) %>% 
    select(-starts_with("SupDem"))

theta.out.df_list_apsr <- map(1:1000, function(x) {
    theta.pe %>% 
        mutate(theta0 = theta.out.t[,x],
               theta = if_else(!is.na(SupDem_trim), theta0, NA_real_)) %>% 
        left_join(sd.apsr, by = c("Country", "Year")) %>% 
        plm::pdata.frame(index = c("Country", "Year"))
})

mod.1_apsr_1k <- map(theta.out.df_list_apsr, function(aDataset) {
    plm(diff(theta, lag=1) ~ plm::lag(theta, 1:2) + diff(Libdem_z, lag=1) 
        + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag=1) + plm::lag(lnGDP_imp, 1), 
        data = aDataset, model="pooling")
})

result_betas_mod.1_apsr_1k <- mitools::MIextract(mod.1_apsr_1k, fun = coef)
result_vars_mod.1_apsr_1k <- mitools::MIextract(mod.1_apsr_1k, fun = vcovBK_se)

mod.1_df_result_cls_apsr_1k <- summary(mitools::MIcombine(results = result_betas_mod.1_apsr_1k,
                                                     variance = result_vars_mod.1_apsr_1k)) %>%
    rownames_to_column(var = "term") %>% 
    rename(conf.low = `(lower`,
           conf.high = `upper)`, 
           estimate = results) %>% 
    filter(!str_detect(term, "(Intercept)")) %>% 
    mutate(model = "Claassen's")
```

```{r apsr_1k_plot}
apsr_1k_plot <- bind_rows(df_result_cls_1k_apsr, mod.1_df_result_cls_apsr_1k) %>% 
  dotwhisker::dwplot() %>% 
  relabel_predictors(c(
    `plm::lag(SupDem_trim, 1:2)1` = "Support[t-1]",
    `plm::lag(SupDem_trim, 1:2)2` = "Support[t-2]",
    `plm::lag(theta, 1:2)1` = "Support[t-1]",
    `plm::lag(theta, 1:2)2` = "Support[t-2]",
    `diff(Liberal_z, lag = 1)` = "Delta~Support(demo~only)",
    `diff(Vdem_liberal_z, lag = 1)` = "Delta~Support(demo~only)",
    `plm::lag(Liberal_z, 1)` = "Support[t-1](demo~only)",
    `plm::lag(Vdem_liberal_z, 1)` = "Support[t-1](demo~only)",
    `diff(Polyarchy_z, lag = 1)` = "Delta~Support(auto~only)",
    `diff(Vdem_polyarchy_z, lag = 1)` = "Delta~Support(auto~only)",
    `plm::lag(Polyarchy_z, 1)` = "Support[t-1](auto~only)",
    `plm::lag(Vdem_polyarchy_z, 1)` = "Support[t-1](auto~only)",
    `diff(Libdem_z, lag = 1)` = "Delta~Liberal~democracy",
    `diff(Vdem_libdem_z, lag = 1)` = "Delta~Liberal~democracy",
    `plm::lag(Libdem_z, 1)` = "Liberal~democracy[t-1]",
    `plm::lag(Vdem_libdem_z, 1)` = "Liberal~democracy[t-1]",
    `diff(lnGDP_imp, lag = 1)` = "Delta~Log~GDP~per~capita",
    `diff(lg_imp_mdpgdp, lag = 1)` = "Delta~Log~GDP~per~capita",
    `plm::lag(lnGDP_imp, 1)` = "Log~GDP[t-1]",
    `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP[t-1]"
)) +
  geom_vline(xintercept = 0, colour = "grey80", linetype = 2) +
  theme_minimal() +
  ggtitle("Dependent Variable: Delta Support for Democracy") + 
  xlab("Coefficient Estimate") +
  scale_color_discrete(name="1k Samples\nDataset", breaks=c("Claassen's","Ours"))

```{r results_comparison_plots, include=TRUE, fig.width=7}
ajps_mean_plot 
ajps_1k_plot
apsr_mean_plot
apsr_1k_plot

```
\pagebreak
